First Order Alternation

### 2018-10-05 quantifiers/draft.tex
ok

Nevertheless, if we require just a yes/no answer (i.e.\ not an
interpolant) recently developped quantifier instantiation heuristics,
such as \cite{ReynoldsKK17}, perform rather well in answering a large
number of queries in this class. Observe, moreover, that coverage does
not need to rely on a complete decision procedure. If the prover fails
in answering the above satisfiability query, then the semi-algorithm
assumes the node is not covered and continues exploring its
successors. Failure to compute complete coverage may lead to
divergence (non-termination) and failure to prove emptiness, but the
soundness of the procedure is preserved.

>>>>

Nevertheless, if we require just a yes/no answer (i.e.\ not an
interpolant) recently developped quantifier instantiation heuristics
\cite{ReynoldsKK17} perform rather well in answering a large number of
queries in this class. Observe, moreover, that coverage does not need
to rely on a complete decision procedure. If the prover fails in
answering the above satisfiability query, then the semi-algorithm
assumes the node is not covered and continues exploring its
successors. Failure to compute complete coverage may lead to
divergence (non-termination) and failure to prove emptiness, but the
soundness of the procedure is not affected.
